Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Use UTF-8 encoding and add linenumbers before abstract
Note link between higher drag coefficient and cross-stream advection; resolves #70
Wosnik edits to abstract

% Add packages and commands to include here
% The amsmath, amsthm, amssymb, hyperref, caption, float and color packages are
% loaded by the MDPI class.
\usepackage{graphicx}
%\usepackage{subfigure,psfig}
\usepackage[draft]{todonotes}
\usepackage{lineno}

@@

% Abstract (Less than 200 words)
\abstract{Experiments were performed with a large laboratory-scale high solidity
    cross-flow turbine to investigate Reynolds number effects on performance and
    wake characteristics, to seek scale thresholds for physical and numerical
    modeling of individual devices and arrays. It was demonstrated that the
    performance of the cross-flow turbine becomes essentially $Re$-independent at a
    Reynolds number based on turbine diameter of $Re_D \approx 10^6$, or an
    approximate Reynolds number based on blade chord of $Re_c \approx 2 \times
    10^5$. A simple model that calculates peak torque coefficient from static foil
    data and cross-flow turbine kinematics was shown to be a reasonable estimator
    for predicting Reynolds number dependence of an actual cross-flow turbine
    operating under dynamic conditions. Mean velocity and turbulence measurements in
    the near-wake showed very subtle differences. However, when transport terms for
    the streamwise momentum and mean kinetic energy were calculated, a similar $Re$
    threshold was revealed. These results imply that physical model studies of
    cross-flow turbines should be $Re_D \sim 10^6$ to properly approximate both the
    performance and wake dynamics of full scale devices and arrays.}

@@

\begin{document}
\linenumbers

@@

Transport due to cross-stream advection appears to become more negative at
higher $Re$. This could be a consequence of increasing free surface deformation
(higher $Fr$), which then decreases the effective flow cross-sectional area
downstream of the turbine, forcing more flow to accelerate around the sides of
the turbine.

>>>>

% Add packages and commands to include here
% The amsmath, amsthm, amssymb, hyperref, caption, float and color packages are
% loaded by the MDPI class.
\usepackage{graphicx}
%\usepackage{subfigure,psfig}
\usepackage[draft]{todonotes}
\usepackage{lineno}
\usepackage[utf8]{inputenc}

@@

\linenumbers

% Abstract (Less than 200 words)
\abstract{Experiments were performed with a large laboratory-scale high solidity
    cross-flow turbine to investigate Reynolds number effects on performance and
    wake characteristics, to establish scale thresholds for physical and numerical
    modeling of individual devices and arrays. It was demonstrated that the
    performance of the cross-flow turbine becomes essentially $Re$-independent at a
    Reynolds number based on turbine diameter of $Re_D \approx 10^6$, or an
    approximate average Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross-flow
    turbine operating under dynamic conditions. Mean velocity and turbulence
    measurements in the near-wake showed subtle differences over the range of $Re$
    investigated. However, when transport terms for the streamwise momentum and mean
    kinetic energy were calculated, a similar $Re$ threshold was revealed. These
    results imply that physical model studies of cross-flow turbines should achieve
    $Re_D \sim 10^6$ to properly approximate both the performance and wake dynamics
    of full scale devices and arrays.}

@@

\begin{document}

@@

Transport due to cross-stream advection appears to become more negative at
higher $Re$. This could be a consequence of increasing free surface deformation
(higher $Fr$), which then decreases the effective flow cross-sectional area
downstream of the turbine, forcing more flow to accelerate around the sides of
the turbine. Note that we also see higher drag coefficients at higher $Re$
(potentially for the same reason), which also helps explain larger negative
values of cross-stream advection.
